---
title: "Project 1"
author: "Jacob Mason"
date: "2025-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This project is a basic exploratory analysis of four facilities with Cost of Non-Conformance and Production data.  This data is completely manufactured (fictonal) but many of the techniques that are used can translate into real projects.  This is for a submission to PSTAT and uses manufactured data because the facility in which I work will not allow any actual data to be released. 



```{r}

getwd()

library(tidyverse)

library(rvest)

library(readxl)

library(ggplot2)

library(gt)

```

```{r}

Data_Path <- "C:/Users/user/Desktop/PSTAT/cost_nonconformance_data.csv"

Cost_NonConformance_Data <- read_csv(Data_Path)

summary(Cost_NonConformance_Data)

print(head(Cost_NonConformance_Data))

#Means <- Cost_NonConformance_Data |> group_by(Facility) |> summarise(mean_cost_nc = mean(`Cost of Non-Conformance (%)`), mean_pro_rate = mean(`Production Rate (%)`))


 ggplot(Cost_NonConformance_Data, aes(x = `Cost of Non-Conformance (%)`, fill = Facility)) +
  geom_density(alpha = 0.6) +
  labs(title = "Distribution of Cost of Non-Conformance by Facility",
       x = "Cost of Non-Conformance (%)",
       y = "Density") +
  theme_minimal()

```


```{r}

ggplot(Cost_NonConformance_Data, aes(x = `Cost of Non-Conformance (%)`, fill = Facility, color = Facility)) +
  geom_density(alpha = 0.4) +
  facet_wrap(~ Facility) +
  labs(title = "Distribution of Cost of Non-Conformance by Facility",
       x = "Cost of Non-Conformance (%)",
       y = "Density") +
  theme_minimal()

```

```{r}
ggplot(Cost_NonConformance_Data, aes(x = Facility, y = `Cost of Non-Conformance (%)`, fill = Facility)) +
  geom_boxplot(alpha = 0.6) +
  labs(title = "Boxplot of Cost of Non-Conformance by Facility",
       x = "Facility",
       y = "Cost of Non-Conformance (%)") +
  theme_minimal() +
  theme(legend.position = "none") 
```

```{r}

summary_stats <- Cost_NonConformance_Data %>%
  group_by(Facility) %>%
  summarise(
    Count = n(),
    Mean = round(mean(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2),
    Median = round(median(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2),
    SD = round(sd(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2),
    Min = round(min(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2),
    Max = round(max(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2)
  )


summary_stats %>%
  gt() %>%
  tab_header(
    title = "Summary Statistics for Cost of Non-Conformance by Facility"
  ) %>%
  fmt_number(
    columns = c(Mean, Median, SD, Min, Max),
    decimals = 2
  ) %>%
  cols_label(
    Count = "Observations",
    Mean = "Mean (%)",
    Median = "Median (%)",
    SD = "Std. Dev (%)",
    Min = "Min (%)",
    Max = "Max (%)"
  ) %>%
  tab_options(
    table.font.size = px(14),
    heading.title.font.size = px(16)
  )


```






