---
title: "Project 1"
author: "Jacob Mason"
date: "2025-02-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This project is a basic exploratory analysis of four facilities with Cost of Non-Conformance and Production data.  This data is completely manufactured (fictonal) but many of the techniques that are used can translate into real projects.  This is for a submission to PSTAT and uses manufactured data because the facility in which I work will not allow any actual data to be released. 



```{r}

getwd()

library(tidyverse)

library(rvest)

library(readxl)

library(ggplot2)

library(gt)

```

```{r}

Data_Path <- "C:/Users/user/Desktop/PSTAT/cost_nonconformance_data.csv"

Cost_NonConformance_Data <- read_csv(Data_Path)

summary(Cost_NonConformance_Data)

print(head(Cost_NonConformance_Data))

#Means <- Cost_NonConformance_Data |> group_by(Facility) |> summarise(mean_cost_nc = mean(`Cost of Non-Conformance (%)`), mean_pro_rate = mean(`Production Rate (%)`))


 ggplot(Cost_NonConformance_Data, aes(x = `Cost of Non-Conformance (%)`, fill = Facility)) +
  geom_density(alpha = 0.6) +
  labs(title = "Distribution of Waste by Facility",
       x = "Waste",
       y = "Density") +
  theme_minimal()

```


```{r}

ggplot(Cost_NonConformance_Data, aes(x = `Cost of Non-Conformance (%)`, fill = Facility, color = Facility)) +
  geom_density(alpha = 0.4) +
  facet_wrap(~ Facility) +
  labs(title = "Distribution of Waste by Facility",
       x = "Waste",
       y = "Density") +
  theme_minimal()

```

```{r}
ggplot(Cost_NonConformance_Data, aes(x = Facility, y = `Cost of Non-Conformance (%)`, fill = Facility)) +
  geom_boxplot(alpha = 0.6) +
  labs(title = "Boxplot of Waste",
       x = "Facility",
       y = "Waste") +
  theme_minimal() +
  theme(legend.position = "none") 
```

```{r}

summary_stats <- Cost_NonConformance_Data %>%
  group_by(Facility) %>%
  summarise(
    Count = n(),
    Mean = round(mean(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2),
    Median = round(median(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2),
    SD = round(sd(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2),
    Min = round(min(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2),
    Max = round(max(`Cost of Non-Conformance (%)`, na.rm = TRUE), 2)
  )


summary_stats %>%
  gt() %>%
  tab_header(
    title = "Summary Statistics for Waste by Facility"
  ) %>%
  fmt_number(
    columns = c(Mean, Median, SD, Min, Max),
    decimals = 2
  ) %>%
  cols_label(
    Count = "Observations",
    Mean = "Mean (%)",
    Median = "Median (%)",
    SD = "Std. Dev (%)",
    Min = "Min (%)",
    Max = "Max (%)"
  ) %>%
  tab_options(
    table.font.size = px(14),
    heading.title.font.size = px(16)
  )


```


```{r}
 ggplot(Cost_NonConformance_Data, aes(x = `Production Rate (%)`, fill = Facility)) +
  geom_density(alpha = 0.6) +
  labs(title = "Distribution of Production by Facility",
       x = "Production Rate (%)",
       y = "Density") +
  theme_minimal()
```


```{r}
ggplot(Cost_NonConformance_Data, aes(x = `Production Rate (%)`, fill = Facility, color = Facility)) +
  geom_density(alpha = 0.4) +
  facet_wrap(~ Facility) +
  labs(title = "Distribution of Production Rate by Facility",
       x = "Production Rate (%)",
       y = "Density") +
  theme_minimal()
```

```{r}
ggplot(Cost_NonConformance_Data, aes(x = Facility, y = `Production Rate (%)`, fill = Facility)) +
  geom_boxplot(alpha = 0.6) +
  labs(title = "Boxplot of Production",
       x = "Facility",
       y = "Production") +
  theme_minimal() +
  theme(legend.position = "none") 
```

```{r}
summary_stats2 <- Cost_NonConformance_Data %>%
  group_by(Facility) %>%
  summarise(
    Count = n(),
    Mean = round(mean(`Production Rate (%)`, na.rm = TRUE), 2),
    Median = round(median(`Production Rate (%)`, na.rm = TRUE), 2),
    SD = round(sd(`Production Rate (%)`, na.rm = TRUE), 2),
    Min = round(min(`Production Rate (%)`, na.rm = TRUE), 2),
    Max = round(max(`Production Rate (%)`, na.rm = TRUE), 2)
  )


summary_stats2 %>%
  gt() %>%
  tab_header(
    title = "Summary Statistics for Production by Facility"
  ) %>%
  fmt_number(
    columns = c(Mean, Median, SD, Min, Max),
    decimals = 2
  ) %>%
  cols_label(
    Count = "Observations",
    Mean = "Mean (%)",
    Median = "Median (%)",
    SD = "Std. Dev (%)",
    Min = "Min (%)",
    Max = "Max (%)"
  ) %>%
  tab_options(
    table.font.size = px(14),
    heading.title.font.size = px(16)
  )

```


```{r}
ggplot(Cost_NonConformance_Data, aes(x = `Production Rate (%)`, y = `Cost of Non-Conformance (%)`)) +
  geom_point(size = 3, alpha = 0.7, color = "blue") +
  labs(title = "Waste vs. Production by Facility",
       x = "Production",
       y = "Waste") +
  theme_minimal() +
  facet_wrap(~Facility)
```


```{r}
correlation_results <- Cost_NonConformance_Data %>%
  group_by(Facility) %>%
  summarize(correlation = cor(`Production Rate (%)`, `Cost of Non-Conformance (%)`, use = "complete.obs"))

# Print the results
print(correlation_results)

correlation_results %>%
  gt() %>%
  tab_header(
    title = md("**Correlation Between Production Rate and Cost of Non-Conformance by Facility**"),
    subtitle = "Pearson correlation coefficients for each facility"
  ) %>%
  fmt_number(
    columns = "correlation",
    decimals = 3
  ) %>%
  cols_label(
    Facility = "Facility",
    correlation = "Correlation with Waste"
  ) %>%
  tab_options(
    table.font.size = "medium",
    heading.align = "center"
  )

```




